---
title       : The new fantastic app, irisApp
subtitle    : An R Slidify presentation
author      : Wei Wei, July 17 2016
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained                # {standalone, draft}
knit        : slidify::knit2slides



---

## When you see an iris, have you wondered which species it might be?

### [The new irisApp][1] will give you the answer


### All you need to is know the length and width of the sepal and the petal

[1]: https://alexindata.shinyapps.io/irisApp/ "The new irisApp"

--- &radio

## Guess the iris species:

It is 5.1cm in sepal length, 3.5cm in sepal width, 1.4cm in petal length, and 0.2cm
in petal width. Check out the hint!

1. virginica
2. versicolor
3. _setosa_

*** .hint
### Enter the numbers into [irisApp][2], and you will have the answer!

[2]: https://alexindata.shinyapps.io/irisApp/ "irisApp"

---

## The iris dataset used for modeling prediction

```{r iris, eval=T, echo=T}
data(iris)
str(iris)
```


---

## Machine learning algorithm used for prediction

### The random forest model

```{r random forest, eval=T, echo=T}
library(randomForest)
data(iris)
set.seed(1234)
ind <- sample(2, nrow(iris), replace = TRUE, prob = c(0.6, 0.4))
training <- iris[ind == 1, ]
testing <- iris[ind == 2, ]
rfMod <- randomForest(Species ~., data=training, importance=TRUE)
predict <- predict(rfMod, testing)
```

### The out-of-sample accuracy of the random forest model 

```{r }
accuracy <- nrow(testing[testing$Species == predict, ]) / nrow(testing)
round(accuracy * 100, 2)
```




